Formal Grammars as Functors and Formal Grammars as Types in Non-commutative Linear-Non-Linear Type Theory

### 2024-01-15 paper/paper.tex
sketch of the canonicity proof

\end{document}

>>>>

Thus we have defined a second model $\gluedNL,\gluedL$ of the type
theory, with a morphism to the syntactic model. By the initiality of
the syntactic model, there is a morphism back to the glued model which
is a section of this projection. For purely positive types, we can
observe by induction on the type structure that the total space of the
family is isomorphic to the set-theoretic semantics. Further, the
projection above defines a section of the families. Finally, by
induction on formulae again we see that this projection is also a
section and therefore an isomorphism, establishing the canonicity
result as stated in Section\ref{section:canonicity}.
\end{document}
